### 2013-09-09 research/paper/results/results-2.3.tex
uploaded 11.03 pm

The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}) was constant beyond $m^*=30$. However, at $m^* \leq 30$ an effect of $m^*$ it could be observed. The peak value of the mean power curve reduces with $m^*$. This may be due to the fact that as the inertia of the system is reduced and galloping becomes weak. Therefore shedding become dominant. This was also reported by \cite{Joly2012} where galloping amplitude was reduced at low $m^*$.

>>>>

The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}) was constant beyond $m^*=30$. However, at $m^* \leq 30$ an effect of $m^*$ it could be observed. Not only the peak value but overall reduction in the mean power could be observed when $m^*$ was reduced.When galloping excitation is suppressed al low $m^*$, the system will exhibit a weak response as a result of forcing from vortex shedding. This was also reported by \cite{Joly2012} where galloping amplitude was reduced at low $m^*$. The suppression of galloping as $m^*$ is reduced can be explained by looking at the difference between the instantaneous power transfer between fluid to the structure $P_t$ and the power taken out by the mechanical damping $P_t$ in \ref{fig:power_time_histories}. While the time avergae of both quantities are the same, instantaneously they are not. Therefore the mechanical system is required to store power in certain points of the cycle and release it at another portion of the cycle. In cases where $m^*$ is very low, the system lack adequate inertia to store this power which leads to suppression of galloping.
